Verification of OpenSSL's SHA3 Keccak function using the Software Analysis Workbench

### 2021-09-14 paper/amended.tex
Update paper.tex and ammended.tex lstlisting.

\begin{figure}[h]
  \centering
  \begin{lstlisting}[basewidth = {.5em}]
1. For all triples (x,y,z) such that 
  0 <= x < 5, 0 <= y < 5, and 0 <= z < w,
  let A'[x, y, z] = A[(x + 3y) mod 5, x, z].
2. Return A'.
  \end{lstlisting}
  \caption{NIST Pi definition}
  \label{fig:nistPi}
\end{figure}

@@

The ‘for’ utility function follows the same intuition as the implementation in most 
imperative languages in that it iterates and runs a loop body over defined elements. 
It is similar to the Array.prototype.map method in JavaScript in that it takes in a 
function and a list of arguments and returns a list of results from calling the function 
on every element of the input array. Figure \ref{fig:cryptolFor} shows it's implementation.

\begin{figure}[h]
  \centering
\begin{lstlisting}[language=Cryptol]
for : {n, a, b} [n]a -> (a -> b) -> [n]b
for vals loop = [loop index | index <- vals]
\end{lstlisting}
\caption{Cryptol For utility function}
\label{fig:cryptolFor}
\end{figure}

@@

\begin{figure}[h]
  \centering
\begin{lstlisting}[basewidth = {.5em}]
1. If t mod 255 = 0, return 1.
2. Let R = 10000000.
3. For i from 1 to t mod 255, let:
  a. R = 0 || R;
  b. R[0] = R[0] ^ R[8];
  c. R[4] = R[4] ^ R[8];
  d. R[5] = R[5] ^ R[8];
  e. R[6] = R[6] ^ R[8];
  f. R =Trunc8[R].
4. Return R[0].
\end{lstlisting}
\caption{NIST RC definition}
\label{fig:nistRC}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{lstlisting}[basewidth = {.5em},basicstyle={\scriptsize}]
1. For all triples (x,y,z) such that 
  0 <= x < 5, 0 <= y < 5, and 0 <= z < w,
  let A'[x, y, z] = A[(x + 3y) mod 5, x, z].
2. Return A'.
  \end{lstlisting}
  \caption{NIST Pi definition}
  \label{fig:nistPi}
\end{figure}

@@

The ‘for’ utility function follows the same intuition as the implementation in most 
imperative languages in that it iterates and runs a loop body over defined elements. 
It recieves a function and a list of arguments and returns a list of results from calling the function 
on every element of the input array. Figure \ref{fig:cryptolFor} shows it's implementation.

\begin{figure}[h]
  \centering
\begin{lstlisting}[language=Cryptol]
for : {n, a, b} [n]a -> (a -> b) -> [n]b
for vals loop = [loop i | i <- vals]
\end{lstlisting}
\caption{Cryptol For utility function}
\label{fig:cryptolFor}
\end{figure}

@@

\begin{figure}[h]
  \centering
\begin{lstlisting}[basewidth = {.5em},basicstyle={\scriptsize}]
1. If t mod 255 = 0, return 1.
2. Let R = 10000000.
3. For i from 1 to t mod 255, let:
  a. R = 0 || R;
  b. R[0] = R[0] ^ R[8];
  c. R[4] = R[4] ^ R[8];
  d. R[5] = R[5] ^ R[8];
  e. R[6] = R[6] ^ R[8];
  f. R = Trunc8[R].
4. Return R[0].
\end{lstlisting}
\caption{NIST RC definition}
\label{fig:nistRC}
\end{figure}
